Linear Prediction of Speech

### 2018-11-15 VM532/HW1/submission.tex
fix choice of thermal conductivity and specific heat, integral of source term still not correct

\section{PROBLEM 2}

>>>>

\section{PROBLEM 2}
When it comes to constant property
\begin{equation}
	\frac{\partial}{\partial y}(k\frac{\partial T}{\partial y}) = k \frac{\partial T^2}{\partial^2 y}
\end{equation}
Since $i=C_p T$ when considering ideal gas
\begin{equation}
	\rho u \frac{\partial i}{\partial x} + \rho v \frac{\partial i}{\partial y} = \rho C_p (u\frac{\partial T}{\partial x} + v \frac{\partial T}{\partial y})
\end{equation}
As $(\frac{\partial u}{\partial y})^2$ is a small term compared to other terms, it can be seen as 0.\\
(Sorry, haven't figured out how to eliminate $\frac{\partial p}{\partial x}$...)

### 2018-11-15 VV556/HW6/submission.tex
fix choice of thermal conductivity and specific heat, integral of source term still not correct

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Methods of Applied Mathematics I\\ HW7 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

@@

\section{Exercise7.1}
	\begin{enumerate}
		\item 
			\begin{proof}
				Since $|\lambda|=1$, then
				\begin{equation}
					||e_\lambda^{(N)}||_2 = \frac{1}{\sqrt{N+1}} \sqrt{\sum_{i=0}^{N} \lambda^{2i}} =  \frac{1}{\sqrt{N+1}} \sqrt{N+1} = 1
				\end{equation}
			\end{proof}
		\item 
			\begin{proof}
				Since
				\begin{equation}
					\begin{aligned}
						(L - \lambda I) e_\lambda^{(N)} 
						& = L e_\lambda^{(N)} - \lambda e_\lambda^{(N)}\\
						& = \frac{1}{\sqrt{N+1}}\big[(\lambda, \lambda^2, ... , \lambda^N, 0, 0, ...) - (\lambda, \lambda^2, ... , \lambda^N, \lambda^{N+1}, 0, ...)\big]\\
						& = \frac{-1}{\sqrt{N+1}}(0, 0, ..., 0, \lambda^{N+1}, 0, ...)
					\end{aligned}
				\end{equation}
				Together with  $|\lambda|=1$, then
				\begin{equation}
				\lim\limits_{N\rightarrow\infty} ||(L - \lambda I) e_\lambda^{(N)}||_2 = \lim\limits_{N\rightarrow\infty} \frac{|\lambda|^{N+1}}{\sqrt{N+1}} = \lim\limits_{N\rightarrow\infty} \frac{1}{\sqrt{N+1}} = 0
				\end{equation}
			\end{proof}
		\item 
			Not figured out...
		\item
			\begin{equation}
				Ru = \lambda u
			\end{equation} 
			Denote $u = (a_0, a_1, ..., a_n, ...)$, then
			\begin{equation}
				\begin{aligned}
					0 &= \lambda a_0\\
					a_0 &= \lambda a_1\\
					...\\
				\end{aligned}
			\end{equation}
	\end{enumerate}

\section{Exercise7.2}
	\begin{enumerate}
		\item 
			\begin{proof}
				Take a subset of the domain of $L^{-1}$, which is denoted as $M$ and is defined as
				\begin{equation}
					M = \Big\{u \in L^2\big([0, 1]\big) \Big| \exists \xi >0 \  \forall x \in [0, \xi] \ u(x) = 0\Big\}
				\end{equation}
				Given any $u(x) \in L^2$, then
				\begin{equation}
					\int_{0}^{1} u^2(x) dx < \infty
				\end{equation}
				Hence $u(x)$ is bounded over $[0, 1]$. \\
				Let 
				\begin{equation}
					T \triangleq \sup \limits_{x\in [0, 1]} |u(x)|
				\end{equation}
				then, $\forall \epsilon > 0$, $\exists v \in M $ s.t.
				\begin{equation}
					v(x) = \Bigg\{\begin{aligned}
					0, &\quad x \in [0, \delta]\\
					u(x), &\quad x \in (\delta, 1]
					\end{aligned}
				\end{equation}
				where $\delta = \frac{\epsilon}{T^2}$. Therefore
				\begin{equation}
					d(u, v) \triangleq ||u-v||_2 = \int_{0}^{1} [u(x) - v(x)]^2 dx = \int_{0}^{\delta} u^2(x) dx \leq T^2 \delta = \epsilon
				\end{equation}
				which indicates that $M$ is dense in $L^2$, so do the domain of $L^{-1}$.
			\end{proof}
		\item 
			\begin{proof}
				\begin{equation}
					||L|| = \sup_{u\in L^2}\frac{||Lu||_2}{||u||_2} = \sup_{u\in L^2}\frac{||xu(x)||_2}{||u(x)||_2} = \sup_{u\in L^2}\frac{|x| ||u||_2}{||u||_2} = \sup_{x\in [0, 1]} |x| = 1
				\end{equation}
				and
				\begin{equation}
					||L^{-1}|| = \sup_{u\in L^2}\frac{||L^{-1}u||_2}{||u||_2} = \sup_{x\in [0, 1]} \frac{1}{|x|} = \infty
				\end{equation}
				hence $L^{-1}$ is unbounded.
			\end{proof}
		\item 
			The state of $L$ is $(I, 1_n)$.\\
			The state of $L^{-1}$ is $(I, 2_c)$.
		\item 
			Yes
		\item 
			Since
			\begin{equation}
				[(L - \lambda I)u] (x) = (Lu)(x) - \lambda u(x) = (x-\lambda) u(x)
			\end{equation}
			The inverse of $(L - \lambda I)$ always exists, therefore $\sigma(L) = \emptyset$.
	\end{enumerate}

\section{Exercise7.3}
	\begin{enumerate}
		\item 
			\begin{proof}
				It's clear that $L^{-1}$ is the differentiate operator, and $L^{-1}$ is unbounded. So $L$ has unbounded inverse.\\
				Since the domain of $L$ is composed of square-integrable functions over $[0,1]$, say
				\begin{equation}
					\int_{0}^{1} f^2(x) dx < \infty
				\end{equation}
				An element within the range of $L$ is
				\begin{equation}
					g(x) = \int_{0}^{x} f(t) dt
				\end{equation}
				Then, if $f(x)$ is a polynomial in $L^2$ , it must be bounded over $[0, 1]$ as it is continous. Denote the supreme of $f(x)$ as $M$, then $g(x) \leq Mx$. Hence $g(x)$ is square-integrable over $[0,1]$, say
				\begin{equation}
					\int_{0}^{1} g^2(x) dx \leq M^2 \int_{0}^{1} x^2 dx < \infty
				\end{equation}
				Clearly, the domain of $L$ doesn't contain all the polynomials and therefore the range of $L$ is open and incomplete. The boundary of the range of $L$ are the limits of squences like $f_n(x) = nx$ when $n\rightarrow \infty$.\\
				Hence, the state of $L$ is $(III, 1_n)$.
			\end{proof}
		\item 
			\begin{equation}
				L^* = L
			\end{equation}

@@

\section{Exercise7.4}
	\begin{proof}
		For $p = 1$
		\begin{equation}
			\begin{aligned}
				RHS & \triangleq ||(a_n)||_1 \cdot ||(b_n)||_1 = \sum_{i=0}^{\infty} |a_i| \cdot \sum_{j=0}^{\infty} |b_j| = \sum_{n=0}^{\infty} \sum_{i+j=n} |a_i||b_j|\\
				 & \geq \sum_{n=0}^{\infty} |\sum_{i+j=n} a_i b_j| = \sum_{n=0}^{\infty} |c_n| = ||(c_n)||_1 \triangleq LHS
			\end{aligned}
		\end{equation} 
		For $p>1$, take $q > 0$ s.t. $\frac{1}{p} + \frac{1}{q} = 1$\\
		Then, using the Holder's inequality
		\begin{equation}
			\begin{aligned}
				LHS & \triangleq ||(c_n)||_p = \Big(\sum_{n=0}^{\infty} |c_n|^p\Big)^{\frac{1}{p}} = \Big(\sum_{n=0}^{\infty} \Big|\sum_{i+j=n}a_i b_j\Big|^p\Big)^{\frac{1}{p}}\\
				& = \Big(\sum_{n=0}^{\infty} \Big|\sum_{i+j=n}a_i b_j^\frac{1}{p} b_j^{\frac{1}{q}}\Big|^p\Big)^{\frac{1}{p}} \leq  \Big(\sum_{n=0}^{\infty} \Big|\sum_{i+j=n}\Big(|a_i| |b_j|^\frac{1}{p}\Big) |b_j|^{\frac{1}{q}}\Big|^p\Big)^{\frac{1}{p}}\\
				& \leq \Big(\sum_{n=0}^{\infty} \Big[\Big(\sum_{i+j=n}|a_i|^p |b_j|\Big)^\frac{1}{p} \Big(\sum_{j=0}^{n}|b_j|\Big)^\frac{1}{q}\Big]^p\Big)^{\frac{1}{p}} \\ 
				& = \Bigg[\sum_{n=0}^{\infty} \Big(\sum_{i+j=n}|a_i|^p |b_j|\Big) \Big(\sum_{j=0}^{n}|b_j|\Big)^\frac{p}{q}\Bigg]^\frac{1}{p} \\
				& \leq \Big(\sum_{i=0}^{\infty}|a_i|^p\Big)^\frac{1}{p}\cdot\Big(\sum_{j=0}^{\infty}|b_j|\Big)^\frac{1}{p}\cdot\Big(\sum_{j=0}^{\infty}|b_j|\Big)^\frac{1}{q}\\
				& = ||(a_n)||_p \cdot ||(b_n)||_1 \triangleq RHS
			\end{aligned}
		\end{equation}
	\end{proof}

>>>>

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Methods of Applied Mathematics I\\ HW6 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

@@

\section{Exercise6.1}
	\begin{enumerate}
		\item
			\begin{proof}
				With the Cauchy-Schwartz inequality
				\begin{equation}
					\sum_{n=1}^{\infty} |y_n|^2 = \sum_{n=1}^{\infty} (\sum_{m=1}^{\infty} a_{nm}x_m)^2 \leq \sum_{n=1}^{\infty} \Big[\sum_{m=1}^{\infty}x_m^2 \sum_{m=1}^{\infty} a_{nm}^2\Big] = \Big(\sum_{m=1}^{\infty}x_m^2\Big) \Big(\sum_{n=1}^{\infty} \sum_{m=1}^{\infty} a_{nm}^2\Big) < \infty
				\end{equation}
				The last setp is valid as $x$ is a square-summable sequence and $\sum_{m,n=1}^{\infty} a_{nm}^2 = M^2 < \infty$.\\
				Hence $y\in l^2$.
			\end{proof}
		\item 
			According to the definition of $L$
			\begin{equation}
				L e_j = (a_{1j}, a_{2j}, ... , a_{nj})
			\end{equation}
			Thus
			\begin{equation}
				L_{ij} = <e_i, L e_j> = a_{ij}
			\end{equation}
		\item 
			\begin{proof}
				Follow from the first part
				\begin{equation}
					||y||_2 \leq ||x||_2 \cdot M
				\end{equation}
				Thus
				\begin{equation}
					||L|| = \sup_{x \in l^2} \frac{||Lx||_2}{||x||_2} \leq \frac{||x||_2 M}{||x||_2} = M
				\end{equation}
			\end{proof}
		\item 
			\begin{proof}
				Denote $(e_j)$ being the standard basis, then
				\begin{equation}
					L e_j = (0, 0, ..., \frac{1}{j}, 0, ... , 0)
				\end{equation}
				Thus
				\begin{equation}
					a_{ij} \triangleq L_{ij} = \delta_{ij}\frac{1}{j}
				\end{equation}
				Hence
				\begin{equation}
					\sum_{n, m = 1}^{\infty} |a_{nm}|^2 = \sum_{n=1}^{\infty} \frac{1}{n^2} = \frac{\pi^2}{6}
				\end{equation}
				which indicates that $L$ is a Hilbert-Schmidt operator.\\
				Let $x_0 = (1, 0, 0, ... , 0)$, then
				\begin{equation}
					||L|| = \sup_{x \in l^2} \frac{||Lx||_2}{||x||_2} \geq \frac{||Lx_0||_2}{||x_0||_2} = \frac{||(1, 0, ...)||_2}{||(1, 0, ...)||_2} = 1
				\end{equation}
				Also, with the Cauchy-Schwartz inequality
				\begin{equation}
					||L|| = \sup_{x \in l^2} \frac{||Lx||_2}{||x||_2} = \sup_{x \in l^2} \frac{\sqrt{\sum_{n=1}^{\infty} (\frac{x_n}{n})^2}}{||x||_2} \leq \sup_{x \in l^2} \frac{\sqrt{\sum_{n=1}^{\infty} x_n^2}}{||x||_2} = \sup_{x \in l^2} \frac{||x||_2}{||x||_2} = 1
				\end{equation}
				Therefore $||L|| = 1$.\\
				It can be seen that $M$ is the upper bound of $||L||$.
			\end{proof}

@@

### 2018-11-15 VV570/HW6/submission.tex
fix choice of thermal conductivity and specific heat, integral of source term still not correct

%----------------------------------------------------------------------------------------
%	PROBLEM 2
%----------------------------------------------------------------------------------------
\section{Integration}

>>>>

%----------------------------------------------------------------------------------------
%	PROBLEM 2
%----------------------------------------------------------------------------------------
\section{Integration}
\begin{enumerate}
	\item 
		The number of nodes is too small s.t. the order of error is too large.
	\item 
		Denote
		\begin{equation}
			E(f) = \int_{a}^{b} f(x)dx - (b-a)f(\frac{a+b}{2})
		\end{equation}
		Thus
		\begin{equation}
			E(1) = (b-a) - (b-a) = 0
		\end{equation}
		\begin{equation}
			E(x) = \frac{b^2-a^2}{2} - (b-a)\frac{b+a}{2} = 0
		\end{equation}
		and
		\begin{equation}
			E(x^2) = \frac{b^3-a^3}{3} - (b-a)(\frac{a+b}{2})^2 \neq 0
		\end{equation}
		Hence, the degree of this quadrature formula is $1$.\\
		The kernel is determined as
		\begin{equation}
			\begin{aligned}
				K_N(t) & = E(x\in [a, b] \rightarrow [(x-t)_+])\\
					   & = \int_{a}^{b} f(x)dx - (b-a)f(\frac{a+b}{2})\\
					   & = \int_{a}^{b} (x-t)_+dx - (b-a)(\frac{a+b}{2}-t)_+\\
					   & = \frac{(b-t)_+^2 + (a-t)_+^2}{2} - (b-a)(\frac{a+b}{2}-t)_+
			\end{aligned}
		\end{equation} 
		Divide the whole range into 4 sub-gap as $(-\infty, a]$,$(a, \frac{a+b}{2}]$,$(\frac{a+b}{2}, b]$,$(b, +\infty)$.
		The non-negative property is seen when examine each gap.
	\item 
		\begin{proof}
			As has been proved above, $k_N(t)$ is non-negative over $[a, b]$, so the first mean value theorem can be applied
			\begin{equation}
				\begin{aligned}
					E(f) & = \frac{1}{N!} \int_{a}^{b}k_N(t)f''(t)dt\\
					     & = f''(\xi) \int_{a}^{b}k_N(t)dt\\
					     & = \frac{(b-a)^3}{24} f''(\xi)
				\end{aligned}
			\end{equation}
		\end{proof}
\end{enumerate}

### 2018-11-15 VV570/HW8/tex/submission.tex
fix choice of thermal conductivity and specific heat, integral of source term still not correct

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages
\usepackage{mathrsfs}
\usepackage{algorithm, algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}} %Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm  
\usepackage{listings}
\lstset{language=Matlab}
\usepackage{enumerate}

@@

%----------------------------------------------------------------------------------------
%	PROBLEM 1
%----------------------------------------------------------------------------------------
\section{Question 1}
	\begin{enumerate}[(a)]
		\item
			It's convex as $f''(x) = e^x > 0$.
		\item 
			It's concave as
			\begin{equation}
				\begin{aligned}
				  RHS-LHS & = t f(x) + (1-t)f(y) - f(tx+(1-t)y)\\
						  & = [t x_1 x_2 + (1-t)y_1 y_2] -[t x_1 + (1-t)y_1][t x_2 + (1-t)y_2]\\
						  & = -t(1-t)(x_1 y_2 + x_2 y_1) < 0
				\end{aligned}
			\end{equation}

@@

%----------------------------------------------------------------------------------------
%	PROBLEM 2
%----------------------------------------------------------------------------------------
\section{Question 2}
	\begin{enumerate}
		\item

	\end{enumerate}
%----------------------------------------------------------------------------------------
%	PROBLEM 3
%----------------------------------------------------------------------------------------
\section{Question 3}
\begin{enumerate}
	\item

\end{enumerate}
%----------------------------------------------------------------------------------------
%	PROBLEM 6
%----------------------------------------------------------------------------------------
\section{Question 6}
	\begin{enumerate}
		\item

@@

>>>>

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages
\usepackage{mathrsfs}
\usepackage{algorithm, algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}} %Use Input in the format of Algorithm  
\renewcommand{\algorithmicensure}{\textbf{Output:}} %UseOutput in the format of Algorithm  
\usepackage{listings}
\lstset{language=Matlab}
\usepackage{enumerate}
\usepackage{graphicx}

@@

\section{Question 1}
	\begin{enumerate}[(a)]
		\item
			It's convex as $f''(x) = e^x > 0$.
		\item 
			Let
			\begin{equation}
				RHS \triangleq t f(x) + (1-t)f(y)
			\end{equation}
			\begin{equation}
				LHS \triangleq - f(tx+(1-t)y)
			\end{equation}
			It's concave as
			\begin{equation}
				\begin{aligned}
				  & RHS-LHS\\
						   = &[t x_1 x_2 + (1-t)y_1 y_2] -[t x_1 + (1-t)y_1][t x_2 + (1-t)y_2]\\
						   = &-t(1-t)(x_1 y_2 + x_2 y_1) < 0
				\end{aligned}
			\end{equation}
		\item 
			Convex.

		\item 
			Convex.

		\item 
			Convex.

		\item 
			Concave.

@@

\section{Question 2}
	\begin{enumerate}[(a)]
		\item 
			\begin{proof}
				Suppose $x = (x_1, x_2, ... , x_m)$, then it's left to prove that
				\begin{equation}
					\frac{\partial f}{\partial x_i} = 0
				\end{equation}
				for $i=1,2, ... , m$ at $x=x^*$.
			\end{proof}
			The partial derivative of $f$ at $x=x^*$ is defined as
			\begin{equation}
				\frac{\partial f}{\partial x_i}\Big|_{x=x^*} = 
				\lim\limits_{\Delta x_i \rightarrow 0}\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i}
			\end{equation}
			Since $f(x^*)$ is the local minimum, $f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) \geq f(x_1, x_2, ... ,x_i^*, ... , x_m)$ however $\Delta x_i$ changes.\\
			Thus
			\begin{equation}
				\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i} \leq 0
			\end{equation} 
			if $\Delta x_i < 0$.\\
			And
			\begin{equation}
				\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i} \geq 0
			\end{equation}  
			if $\Delta x_i > 0$.\\
			Hence, $\frac{\partial f}{\partial x_i}\Big|_{x=x^*} = 0$ as $f$ is continuously differentiable.
			Therefore, $\triangledown f(x^*) =0$.
		\item 
			\begin{proof}
				With taylor expansion of $f(x)$ at $x=x^*$
				\begin{equation}
					\begin{aligned}
						  &f(x) - f(x^*) \geq 0 \quad \quad (\text{$f(x^*)$ is the local minimum})\\
		  \Leftrightarrow &\triangledown f(x^*) \Delta x + \frac{1}{2} \Delta \xi H(x^*) \Delta \xi ^T \geq 0\\
		  \Leftrightarrow &\frac{1}{2} \Delta \xi H(x^*) \Delta \xi ^T \geq 0 \quad \quad (\text{gradient be 0})
					\end{aligned}
				\end{equation}
				where $d(\Delta \xi, x^*) \leq d(x, x^*)$, and the gradient is $0$ as been proved above.
				Thus, $ \Delta \xi H(x^*) \Delta \xi ^T \geq 0$ for any $\Delta \xi$ within the local neighbourhood of $x=x^*$.\\
				Hence $H(x^*)$ is semi-positive finite.

			\end{proof}
		\item 
			\begin{proof}
				($\Leftarrow$)The global minimum must be a local minimum, and the gradient is therefore 0 as $f$ is differentiable.

				($\Rightarrow$)As has been proved above, $\triangledown f(x^*)=0$ indicates that $f(x^*)$ is the local minimum. It's left to prove that local minimum is also global minimum for a convex function.
				Suppose there exist $x'$ s.t. 
				\begin{equation}
					f(x') < f(x^*)
				\end{equation}
				Then, by convexity
				\begin{equation}
					f(t x' + (1-t)x^*) \leq t f(x') + (1-t) f(x^*) < \leq t f(x^*) + (1-t) f(x^*) = f(x^*)
				\end{equation}
				When $t\rightarrow1$, the inequality above contradicts local optimality of $x^*$.\\
				Thus, the assumption fails, which indicates that $f(x^*)$ is the global minimum for $f$.

			\end{proof}
		\item
			\begin{proof}
				($\Rightarrow$)By Taylor expansion
				\begin{equation}
					f(x+ d) = f(x) + \triangledown f(x) d + \frac{1}{2} d^T H(x) d + O(||d||^2)
				\end{equation}
				If the Hessian matrix $H$ is semi-definite positive, then
				\begin{equation}
					d^T H(x) d \geq 0
				\end{equation}
				Thus
				\begin{equation}
					f(x+ d) \geq f(x) + \triangledown f(x) d
				\end{equation}
				which is the so called 1-st order condition, and it implies that the function $f$ is convex.

				($\Leftarrow$)By Taylor expansion
				\begin{equation}
					f(x+ t d) = f(x) + t \triangledown f(x) d + \frac{t^2}{2} d^T H(x) d + O(||d||^2)
				\end{equation}
				With the 1-st order condition
				\begin{equation}
					f(x+ t d) \geq f(x) + t \triangledown f(x) d
				\end{equation}
				Thus
				\begin{equation}
					\frac{t^2}{2} d^T H(x) d + O(t||d||^2) \geq 0
				\end{equation}
				Dividing it by $\frac{t^2}{2}$ and set $t \rightarrow 0$, it gives out that for any $d\in \mathbb{R}^n$, $d^T H(x) d \geq 0$.

			\end{proof}

@@

\section{Question 4}
	The genetic algorithm is adopted as there exists intensive oscillation when $x$ approaches $0$, and optimization algorithms dependent on the gradient info are easy to fall into local minimum.\\
	The global minimum found is $x_0=0.217, f(x_0)=-0.0249$.

\section{Question 6}
	The plot of $g(y)$ is given as follows
	\begin{figure}[!htbp]
		\centering
		\includegraphics[width=15cm]{../pic/Task6.eps}
	\end{figure}

\section{Question 7}
	According to the geometric relations, the allowable length of the ladder is given as
	\begin{equation}
		L(\alpha) = \min\limits_{\beta} (\frac{1}{sin(\beta)} + \frac{1}{sin(\alpha + \beta)})
	\end{equation}
	By solving the minimisation problem, the plot of $L$ versus $\alpha$ is given as follows
	\begin{figure}[!htbp]
		\centering
		\includegraphics[width=15cm]{../pic/Task7.eps}	
	\end{figure}

### 2018-11-15 VV570/HW9/tex/submission.tex
question2 ok
fix choice of thermal conductivity and specific heat, integral of source term still not correct

\section{Question 2}
	\begin{enumerate}[(a)]
		\item

@@

\section{Question 4}

\section{Question 6}

>>>>

\section{Question 2}
	\begin{enumerate}[(a)]
		\item 
			As $\Phi(t, y) = arctan(y)$, then
			\begin{equation}
				\Bigg| \frac{\partial \Phi}{\partial y} \Bigg| = \frac{1}{|1+y^2|} < 1 \triangleq c
			\end{equation}
		\item 
			As $\dot{y} = \Phi(t, y) = arctan(y)$, then
			\begin{equation}
				|\ddot{y}| = \Bigg| \frac{\dot{y}}{1+y^2} \Bigg| = \frac{|arctan(y)|}{1+y^2} < \frac{\pi}{2(1+y^2)} \leq \frac{\pi}{2} 
			\end{equation}
		\item 
			As the global error is bounded by
			\begin{equation}
				|e_k| \leq \frac{\tau^*}{hc}[e^{c(t_k - t_0)} - 1]
			\end{equation}
			where $\tau^* = \max\limits_{k}|\tau_k|$, $c$ is the Lipschitz constant and is taken as $1$ as has been illustrated above.\\
			Since 
			\begin{equation}
				\begin{aligned}
					\frac{\tau^*}{h} & = \max\limits_{k}\Bigg|\frac{y(t_k) - y(t_{k-1}) - h\Phi(t_{k-1}, y(t_{k-1}))}{h}\Bigg|\\
									 & \leq \max\limits_{k}\Bigg| \frac{y(t_k) - y(t_{k-1})}{h}\Bigg| + |\Phi(t_{k-1}, y(t_{k-1}))|\\
									 & = 2 \max\limits_{k} |\Phi(t_{k-1}, y(t_{k-1}))| < \pi
				\end{aligned}
			\end{equation}
			Thus, $|e_k| < \pi[e^{(t_k - t_0)}-1]$.
	\end{enumerate}

\section{Question 3}
	\begin{enumerate}[(a)]
		\item 
			With $y_0 = 4$, $y_k$ are calculated using Euler's method as follows
			\begin{equation}
				y_k = y_{k-1} + h \Phi(t_{k-1}, y_{k-1})
			\end{equation}
			The calculation is carried out with matlab, and the results are given as below
			\begin{figure}[!htbp]
				\centering
				\includegraphics[width=8cm]{../pic/Q3_a.eps}
			\end{figure}
		\item 
			The initial value of $y_k^{(0)}$ is calculated using Euler's method.\\
			Then $y_k^{(i)}$ are calculated in $i-th$ iteration, and the back-ward Euler's method is adopted.
			\begin{equation}
				y_k^{(i)} = y_{k-1}^{(i)} + h \Phi(t_{k}, y_k^{(i-1)})
			\end{equation} 
			The calculation is carried out with matlab, and the results are given as below
			\begin{figure}[!htbp]
				\centering
				\includegraphics[width=8cm]{../pic/Q3_b.eps}
			\end{figure}
		\item 
			Iteration formula is given as 
			\begin{equation}
				y_k = y_{k-1} + h \Phi(t_{k-1}, y_{k-1}) + \frac{h^2}{2}[\Phi_t(t_{k-1}, y_{k-1}) + \Phi_y(t_{k-1}, y_{k-1}) \Phi(t_{k-1}, y_{k-1})]
			\end{equation}
			The calculation is carried out with matlab, and the results are given as below
			\begin{figure}[!htbp]
				\centering
				\includegraphics[width=8cm]{../pic/Q3_c.eps}
			\end{figure}
		\item 
			The calculation is carried out with the prediction-correction method. Iteration formulas are given as
			\begin{equation}
				y^* = y_{k-1} + h \Phi(t_{k-1}, y_{k-1})
			\end{equation}
			\begin{equation}
				y_k = y_{k-1} + \frac{h}{2} [\Phi(t_{k-1}, y_{k-1}) + \Phi(t_k, y^*)] 
			\end{equation}
			The calculation is carried out with matlab, and the results are given as below
			\begin{figure}[!htbp]
				\centering
				\includegraphics[width=8cm]{../pic/Q3_d.eps}
			\end{figure}
		\item 
			Here, an extra initial point($y_1$) is required, and it is calculated using the Euler's method as
			\begin{equation}
				y_1 = y_0 + h \Phi(t_0, y_0)
			\end{equation}
			Then, the iteration steps are taken as
			\begin{equation}
				y_k = y_{k-1} + \frac{h}{2}[3\Phi(t_{k-1}, y_{k-1}) - \Phi(t_{k-2}, y_{k-2})]
			\end{equation}
			The calculation is carried out with matlab, and the results are given as below
			\begin{figure}[!htbp]
				\centering
				\includegraphics[width=8cm]{../pic/Q3_e.eps}
			\end{figure}

@@

### 2018-11-15 VV570/PROJ1/article/article.tex
fix choice of thermal conductivity and specific heat, integral of source term still not correct

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
%% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

@@

%use graph format
\usepackage{graphicx} 
\usepackage{epstopdf}

@@

\begin{abstract}
%% Text of abstract
A model was established for predicting a speech linearly. Two strategies are developed to determine the coefficients. One is windowing the error and the Cholesky decomposition is applied. The other is windowing the signal and the Topelitz equations are solved iteratively. The two strategies are compared using a sample speech finally.
\end{abstract}

\begin{keyword}
Speech \sep Prediction \sep Cholesky \sep Topelitz
%% keywords here, in the form: keyword \sep keyword

@@

\subsection{Relation between the error and $p$}

@@

%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}          ==>>  [#]
%%   \cite[chap. 2]{key} ==>>  [#, chap. 2]
%%   \citet{key}         ==>>  Author [#]

%% References with bibTeX database:

\bibliographystyle{model1-num-names}
\bibliography{sample.bib}

%% Authors are advised to submit their bibtex database files. They are
%% requested to list a bibtex style file in the manuscript if they do
%% not want to use model1-num-names.bst.

%% References without bibTeX database:

% \begin{thebibliography}{00}

%% \bibitem must have the following form:
%%   \bibitem{key}...
%%

% \bibitem{}

% \end{thebibliography}

@@

%%
%% End of file `elsarticle-template-1-num.tex'.

>>>>

\usepackage{cite}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}
\usepackage{epstopdf}

@@

@@

\begin{abstract}
%% Text of abstract
A model was established for predicting a speech linearly. Two strategies are developed to determine the coefficients. One is windowing the signal and the Topelitz equations are solved iteratively. The other is windowing the error and the Cholesky decomposition is applied. Both the two strategies are compared with a sample speech finally.
\end{abstract}

\begin{keyword}
Speech Prediction \sep Correlation \sep Covariance \sep Cholesky \sep Topelitz
%% keywords here, in the form: keyword \sep keyword

@@

\subsection{Relation between the error and $p$}
Here, the covariance method is choosen for further investigating the relation between the error and the prediction order $p$.

Again, the total number of samples is fixed($len = 120$). The error vector $e$ is measured with $\lVert e \rVert_2$. $p$ is equidistantly choosen ranging from $2$ to $50$. Plot indicating the relation between the order of error and $p$ is given as below.

\begin{figure}[!h]
	\centering
	\includegraphics[height=5.5cm,width=9cm]{../pic/err_vs_p.eps}
\end{figure}

It can be seen from the plot that the error is reduced immediately when $p$ is increased from $5$ to $15$, but the error decreases slowly when $p$ continues to grow.

\section{Conclusion}
Two different methods were introduced to calculate the linear prediction coefficients. Numerical experiments were carried out to compare the performence of these two methods, and the results show that the covariance method
does better than the correlation method. Possible reasons were suggested and a further study on the relation between the error and $p$ indicates that the error decreases intensively at the begining but tends to be converged later on.

@@

\bibliographystyle{plain}
\bibliography{article.bib}

@@
